Software Citation Principles

### 2016-03-22 sc-principles/software-citation-principles.tex
fix typo

Most noteable of the community efforts are those of WSSSPE~\cite{wssspe} and SSI~\cite{ssi-workshops} who between them have run a series of workshops aimed at gathering together community memberrs with an interest in improving the status of software in academia. \asnote{Not sure this is a sufficient one-line summary but couldn't think of anything better.} In each of the three years that WSSSPE workshops have run thus far, the participants have produced a report documenting the topics covered. Section 5.8 and Appendix J in \cite{WSSSPE3} has some preliminary work and discussion particularly relevant to this working group.

>>>>

Most noteable of the community efforts are those of WSSSPE~\cite{wssspe} and
SSI~\cite{ssi-workshops} who between them have run a series of workshops aimed
at gathering together community members with an interest in improving the
status of software in academia. \asnote{Not sure this is a sufficient one-line
summary but couldn't think of anything better.} In each of the three years that
WSSSPE workshops have run thus far, the participants have produced a report
documenting the topics covered. Section 5.8 and Appendix J in \cite{WSSSPE3}
has some preliminary work and discussion particularly relevant to this working
group.
